Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-15 main.tex
Updates from Overleaf

We also have access to the observation of $x(t)$ and to noisy a measurement of $\dot{x}(t)$ in the form
$
    \dot{x}(t) + C\nu(t)
$ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known.
For better readability, we will actually denote the measurement as:
\begin{equation}
\label{eq:measurement}
    y(t) = \dot{x}(t) - A_0 x(t) - Bu(t) + C\nu(t)
\end{equation}
which is possible since the nominal dynamics $A_0$, thet state $x(t)$ and the control $u(t)$ are known.
Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.

@@

\paragraph{Objective}
Having observed at times a history of transitions $\cD = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
\begin{align}
\probability{A(\theta)\in \cC_\delta} \geq 1-\delta
\label{eq:polytope}
\end{align}

@@

To that end, we further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
\begin{assumption}[Linear parametrisation]
\label{assumpt:linear_param}
There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
\begin{equation}
    A(\theta) = A_0 + %\theta^\transp \phi \eqdef A_0 + 
    \sum_{i=1}^d \theta_i\phi_i
\end{equation}
where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
\end{assumption}

\paragraph{Regularised least square} Since we expect that $\Phi_n$ may have zero-coordinates during possibly long time intervals (i.e. some features are not always active), we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:

@@

\begin{theorem}[Regularised solution]
\label{thm:regularized_solution}
The solution to \eqref{eq:regression_min} is:
\begin{equation}
    \label{eq:vector_rls}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n
\end{equation}
where 
\begin{equation*}
    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
\end{equation*}
\end{theorem}

@@

With Hölder inequality, we obtain a confidence region $\cC$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
\begin{equation}
\begin{split}
\label{eq:bounded-noise-polytope}
\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty
\end{split}
\end{equation}

@@

\begin{theorem}[Confidence ellipsoid]
Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
\begin{align}
    \label{eq:confidence-ellipsoid}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
     + \lambda^{1/2}\|\theta\|_2.
\end{align}
\label{thm:confidence_ellipsoid}

\end{theorem}

\begin{lemma}[Confidence polytope]
\label{lem:confidence_polytope}
We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &G_{N,\lambda}^{-1} = PDP^{-1}\\
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
    &A_0 = \theta_{N,\lambda}^\transp\Phi\\
    &\Delta A_k = \Delta\theta_k^\transp\Phi
\end{align*}
This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
\end{lemma}

@@

Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
% \begin{gather*}
% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
% \end{gather*}
% where{\footnotesize{}
% \begin{gather*}
% \Upsilon=\left[\begin{array}{cccc}
% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
% P & Z_{+} & Z_{-} & -\Gamma
% \end{array}\right],\\
% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
% \mathcal{A}=\left[\begin{array}{cc}
% A_{0} & 0\\
% 0 & A_{0}
% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
% 0 & -\Delta A_{-}\\
% 0 & \Delta A_{+}
% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
% \Delta A_{+} & 0\\
% -\Delta A_{-} & 0
% \end{array}\right],
% \end{gather*}
% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

@@

We consider the robust control objective $v^r$:

\begin{equation}
\label{eq:robust-control}
\max_\bu \underbrace{\min_{A(\theta) \in \cP} \left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t, \omega(t)\right]}_{v^r(\bu)}
\end{equation}

\begin{definition}[Surrogate objective]
We approximate the robust objective $v^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the polytopic approximation $\cP_\delta$ of $A(\Theta)$:

\begin{equation}
\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x)
\end{equation}
where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

@@

\begin{proposition}[Lower bound]
\label{prop:lower-bound}
With high probability, the surrogate objective $\hat{v}^r$ is a lower bound of the true objective $v^r$:

\begin{equation}
\hat{v}^r(\bu) \leq v^r(\bu)
\end{equation}

If we assume that $R$ is $L$-Lipschitz, then we can also bound the approximation error:
\begin{equation*}
     v^r(\bu) - \hat{v}^r(\bu) \leq L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
\end{equation*}
\end{proposition}

@@

\section{Multi-model Estimation and Control}

What if our system dynamics \eqref{eq:dynamics} or linear parametrisation assumption \ref{assumpt:linear_param} are wrong?

\subsection{Model adequacy}

@@

The simple regret of the action $a$ returned by Algorithm \ref{algo:drop} after $n$ rounds is defined as:
\begin{equation}
\mathcal{R}_n = v^r - v_a^r
\end{equation}
We will say that $\mathcal{R}_n=O(\varepsilon)$ for some $\varepsilon>0$ if there exist $\rho>0$ and $n_0>0$ such that $\mathcal{R}_n\leq\rho\varepsilon$ for all $n\geq n_0$.
A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $v_i^r \geq v^r - \epsilon$ for some $\epsilon > 0$. The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$. Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:
\begin{assumption}[Proportion of near-optimal nodes]
\label{assumpt:beta}
There exist $\beta\in[0, \frac{\log K}{\log 1/\gamma}]$, $c > 0$ and $d_0 > 0$ such that $p_d(\epsilon)\leq c\epsilon^\beta$ for all $\epsilon > 0$ and $d\geq d_0$.
\end{assumption}

\begin{theorem}[Regret bound]
\label{theorem:drop-regret}
Let $\kappa = K\gamma^\beta \in [1, K]$. Then the simple regret of Algorithm \ref{algo:drop} is:

\begin{equation}
\text{If } \kappa>1,\qquad 
\mathcal{R}_n = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
\end{equation}

\begin{equation}
\text{If }\kappa=1,\qquad
\mathcal{R}_n = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}n}\right)
\end{equation}
\end{theorem}

@@

\subsection{Proof of \autoref{thm:regularized_solution}}

@@

\subsection{Proof of \autoref{lem:confidence_polytope}}

@@

\begin{proof}
We have that $A(\theta) \in \cP$ with probability $1-\delta$. Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$. This gives the following bound:
\begin{equation*}
 \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
\end{equation*}

@@

>>>>

We also have access to the observation of $x(t)$ and to noisy a measurement of $\dot{x}(t)$ in the form
$
    \dot{x}(t) + C\nu(t)
$ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.

@@

\paragraph{Objective}
Having observed at times a history of transitions $\cD_{[N]} = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
\begin{align}
\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
\label{eq:polytope}
\end{align}

@@

To that end, we further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
\begin{assumption}[Linear parametrisation]
\label{assumpt:linear_param}
There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
\begin{equation}
    A(\theta) = A + %\theta^\transp \phi \eqdef A + 
    \sum_{i=1}^d \theta_i\phi_i
\end{equation}
where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
\end{assumption}

For readability, we denote the noisy measurement of $\dot{x}$ as:
\begin{equation}
\label{eq:measurement}
    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t)
\end{equation}
which is possible since the nominal dynamics $A$, the state $x(t)$ and the control $u(t)$ are known.
Thus, we obtain the system
\[
y_n = \Phi_n\theta + \eta_n
\]

\paragraph{Regularised least square} We consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:

@@

\begin{proposition}[Regularised solution]
\label{prop:regularized_solution}
The solution to \eqref{eq:regression_min} is:
\begin{equation}
    \label{eq:vector_rls}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n
\end{equation}
where 
\begin{equation*}
    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
\end{equation*}
\end{proposition}

@@

By Hölder inequality, we obtain a confidence region $\cC_\delta$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
\begin{equation}
\begin{split}
\label{eq:bounded-noise-polytope}
\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty
\end{split}
\end{equation}

@@

\begin{theorem}[Confidence ellipsoid]
Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
\begin{align}
    \label{eq:confidence-ellipsoid}
    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} \leq \beta_N(\delta),
\end{align}
with
\begin{equation}
    \beta_N(\delta)\eqdef \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
     + \lambda^{1/2}\|\theta\|_2.
\end{equation}
\label{thm:confidence_ellipsoid}
\end{theorem}

We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_\delta$. For simplicity, we present here a very simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and the sphere by its enclosing hypercube:
\begin{align}
    \label{eq:generic-polytope}
     &\cC_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\},\\
     &A_0 = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = h_i \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
\end{align}

Another strategy presented in \autoref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalization of $G_{N,\lambda}$.

@@

% Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
% \begin{gather*}
% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
% \end{gather*}
% where{\footnotesize{}
% \begin{gather*}
% \Upsilon=\left[\begin{array}{cccc}
% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
% P & Z_{+} & Z_{-} & -\Gamma
% \end{array}\right],\\
% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
% \mathcal{A}=\left[\begin{array}{cc}
% A_{0} & 0\\
% 0 & A_{0}
% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
% 0 & -\Delta A_{-}\\
% 0 & \Delta A_{+}
% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
% \Delta A_{+} & 0\\
% -\Delta A_{-} & 0
% \end{array}\right],
% \end{gather*}
% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency. Among interval prediction algorithms, this predictor tends to produce tighter and more stable predictions than other candidates, and its stability can be assessed simply in terms of LMI.

@@

At time $N$, we denote the vector of future controls as $\bu = (u_{N+1},u_{N+2},\cdots)$ and future perturbations as $\bw = (\omega_N, \omega_{N+1},\cdots)$.

We consider the robust control objective $V^r$:

\begin{equation}
\label{eq:robust-control}
\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
\end{equation}

\begin{definition}[Surrogate objective]
We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$:

\begin{align}
\underline{R}(t,\bu) \eqdef \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x) \\
\hat{V}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \underline{R}(t,\bu) \label{eq:surrogate_objective}
\end{align}
where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

@@

\begin{proposition}[Lower bound]
\label{prop:lower-bound}
With high probability, the surrogate objective $\hat{V}^r$ is a lower bound of the true objective $V^r$:

\begin{equation}
\hat{V}^r(\bu) \leq V^r(\bu)
\end{equation}
\end{proposition}

@@

\begin{proposition}
\label{prop:control-error}
If we assume that the reward function $R$ is lipschitz, then we can bound the approximation error:
\begin{equation*}
     V^r(\bu) - \hat{V}^r(\bu) = \cO\left(\frac{1}{\sqrt{N}}\right)
\end{equation*}
\end{proposition}

\begin{algorithm}[tb]
   \caption{Robust Estimation, Prediction and Control}
   \label{alg:full}
\begin{algorithmic}
   \STATE {\bfseries Input:} confidence level $\delta$
   \FOR{$N = 1,2,3,\dots$} 
   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
   \FOR{planning steps $[T]$}
   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval_predictor} using $\cC_{[N],\delta}$.
   \ENDFOR
   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
   \ENDFOR

\end{algorithmic}
\end{algorithm}

\section{Multi-model Extension}

The procedure we developed in sections relies on several modelling assumptions which can be quite restrictive, such as the system dynamics \eqref{eq:dynamics} or its linear parametrisation in \autoref{assumpt:linear_param}. But what if they are wrong?

\paragraph{Model adequacy}

@@

We introduce a measure of the problem difficulty: TODO: Definition of $\kappa\in [1, K]$
A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $V_i^r \geq V^r - \epsilon$ for some $\epsilon > 0$. The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$. Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:

\begin{theorem}[Regret bound]
\label{theorem:drop-regret}
The simple regret of Algorithm \ref{algo:drop} after $T$ iterations is:

\begin{equation}
\text{If } \kappa>1,\qquad 
v^r - v^r_{a_T} = O\left(T^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
\end{equation}

\begin{equation}
\text{If }\kappa=1,\qquad
v^r - v^r_{a_T} = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}T}\right)
\end{equation}
\end{theorem}

@@

\subsection{Proof of \autoref{prop:regularized_solution}}

@@

@@

\begin{proof}
We have that $A(\theta) \in \cC_{[N],\delta}$ with probability $1-\delta$. Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$. This gives the following bound:
\begin{equation*}
 \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
\end{equation*}

@@

\subsection{Tighter conversion form ellipsoid to polytope}
\label{sec:tight-polytope}
\begin{lemma}[Confidence polytope]
\label{lem:tight_polytope}
We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
\begin{equation}
     \cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
    &G_{N,\lambda}^{-1} = PDP^{-1}, \quad \Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k, \\
    &A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
\end{align*}
This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
\end{lemma}
